Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-26 Thesis/chapter/063-discussion.tex
change from article to report

\subsection{Hindsight is easier than foresight}
%\subsection{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?: sation vs zation} 
This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
%\subsubsection{Research, exploration and design phase}
%\subsubsection{Narrowing, pre-optimisation and constraint phase}
%\subsubsection{Optimisation, modelling and data generation}
%\subsubsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Research, exploration and design phase}
\label{sec:phase1}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

\subsubsection{Narrowing, pre-optimisation and constraint phase}

@@

\subsubsection{Optimisation, modelling and data generation}

@@

\subsubsection{Evaluation, interpretation and outlook phase}

@@

%Issues of methods for learning from data: 
%\begin{itemize}
%	\item How to incorporate a priori assumptions into learning? 
%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
%	\item How to find a optimal balance between the data and a priori knowledge? 
%\end{itemize}
%\cite{cherkassky1998learning}
%"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
%"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps. 
%Any learning process requires the following(p40): 
%\begin{itemize}
%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
%	\item A priori knowledge to impose contrains
%	\item An inductive principle (what needs to be done)
%		\begin{itemize}
%			\item penalizeation (regularization) inductive principle
%			\item early stopping rules (with ANN, difficult to control and interpret)
%			\item structural risk minimization (SRM) (order according to complexity)
%			\item Bayesian Inference (add subjectivity to learning machine)
%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
%		\end{itemize}
%	\item A learning method (how does it need to be done,implementation)
%\end{itemize}
%\cite{cherkassky1998learning}
%am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
%Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{LINKS}
%\begin{itemize}
%    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
%    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
%    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
%\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?: sation vs zation} 
This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
%\subsection{Research, exploration and design phase}
%\subsection{Narrowing, pre-optimisation and constraint phase}
%\subsection{Optimisation, modelling and data generation}
%\subsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

\subsection{Narrowing, pre-optimisation and constraint phase}

@@

\subsection{Optimisation, modelling and data generation}

@@

\subsection{Evaluation, interpretation and outlook phase}

@@

%Issues of methods for learning from data: 
%\begin{itemize}
%	\item How to incorporate a priori assumptions into learning? 
%	\item How to measure model complexity (i.e. flexibility to fit the training data)?
%	\item How to find a optimal balance between the data and a priori knowledge? 
%\end{itemize}
%\cite{cherkassky1998learning}
%"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}
%"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)
%"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)
%Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
%Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps. 
%Any learning process requires the following(p40): 
%\begin{itemize}
%	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
%	\item A priori knowledge to impose contrains
%	\item An inductive principle (what needs to be done)
%		\begin{itemize}
%			\item penalizeation (regularization) inductive principle
%			\item early stopping rules (with ANN, difficult to control and interpret)
%			\item structural risk minimization (SRM) (order according to complexity)
%			\item Bayesian Inference (add subjectivity to learning machine)
%			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
%		\end{itemize}
%	\item A learning method (how does it need to be done,implementation)
%\end{itemize}
%\cite{cherkassky1998learning}
%am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
%Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{LINKS}
%\begin{itemize}
%    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
%    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
%    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
%\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
